A Spiking Independent Accumulator Model for Winner-Take-All Computation

### 2017-02-01 doc/paper/paper.tex
Do not balance last column.
Fix plural in Notes.
Also fixes and undefull hbox.
Update network names in notebooks.
Closes #1.
Fix grammar in sentence.

\usepackage{cogsci}
\usepackage{commath}
\usepackage{graphicx}
\usepackage{pslatex}
\usepackage{siunitx}
\usepackage{apacite}
\usepackage{xcolor}  % for \textcolor
\usepackage{flushend}  % balance final column height

@@

We implement Equation~\ref{eqn:usher-mcclelland} with the NEF by using one population of neurons for each $x_i$, and applying Principle~3 to each population.
By appropriately selecting the gain and bias parameters from Principle~1, we ensure that each state variable is rectified ($x_i \ge 0$) as required.
We believe this implementation is novel as it does not interpret each $x_i$ as a distinct neural firing rate, but rather as a population-level representation distributed across any number of spiking neurons.
In effect, heterogeneous spike trains are weighted by optimal decoding weights to precisely implement the stated dynamics.
%As such, the model equations do not impose restrictions on the neuron model or requires to lump the neurons into a single population firing rate.
This allows us to attain greater biological realism without altering the dynamics prescribed by Equation~\ref{eqn:usher-mcclelland}.
\begin{figure}[t]
    \centering
    \includegraphics{figures/usher-mcclelland}\\
    \vspace*{.3cm}
    \includegraphics{figures/indacc}
    \caption{
        Example time course of the state variables in the LCA (top) and IA (bottom) networks with three choices ($D~=~3$).
        The vector of inputs is $\left[ 0.8, 0.7, 0.6 \right]$.
    }\label{fig:usher-mcclelland}\label{fig:indacc}
\end{figure}

@@

\section{Discussion}
We have shown that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
For instance, the LCA network can determine the correct winner more quickly, and, given that a conclusive decision was made, it always selects the correct winner.
However, under noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
This can be problematic for cognitive models that must form a clear decision (even when it may be incorrect).
The IA network might not be able to identify the correct winner as quickly or as reliably (depending on the choice of $\tau_1$), but given enough time it will eventually arrive at a decision and produce a clear output.
This is a direct consequence of the thresholding on the state feedback, which prevents competition from occurring until a sufficient amount of evidence has accumulated.
This also enables the IA network to react to small inputs.
In addition, the IA network is easily extendible to allow dynamic control the speed of decisions, by supplying an external bias to layer 2 to adjust the $\vartheta$ threshold.

@@

\section{Notes}
Source code and supplementary analysis is available at \url{https://github.com/ctn-waterloo/cogsci17-decide}.
%These have not been peer reviewed.

>>>>

\usepackage{cogsci}
\usepackage{commath}
\usepackage{graphicx}
\usepackage{pslatex}
\usepackage{siunitx}
\usepackage{apacite}
\usepackage{xcolor}  % for \textcolor

@@

We implement Equation~\ref{eqn:usher-mcclelland} with the NEF by using one population of neurons for each $x_i$, and applying Principle~3 to each population.
By appropriately selecting the gain and bias parameters from Principle~1, we ensure that each state variable is rectified ($x_i \ge 0$) as required.
We believe this implementation is novel as it does not interpret each $x_i$ as a distinct neural firing rate, but rather as a population-level representation distributed across any number of spiking neurons.
In effect, heterogeneous spike trains are weighted by optimal decoding weights to precisely implement the stated dynamics.
%As such, the model equations do not impose restrictions on the neuron model or requires to lump the neurons into a single population firing rate.
This allows us to attain greater biological realism without altering the dynamics prescribed by Equation~\ref{eqn:usher-mcclelland}.
\begin{figure}[t]
    \centering
    \includegraphics{figures/lca}\\
    \vspace*{.3cm}
    \includegraphics{figures/ia}
    \caption{
        Example time course of the state variables in the LCA (top) and IA (bottom) networks with three choices ($D~=~3$).
        The vector of inputs is $\left[ 0.8, 0.7, 0.6 \right]$.
    }\label{fig:usher-mcclelland}\label{fig:indacc}
\end{figure}

@@

\section{Discussion}
We have shown that neither network performs better on all benchmarks, but rather each is better suited for different purposes.
For instance, the LCA network can determine the correct winner more quickly, and, given that a conclusive decision was made, it always selects the correct winner.
However, under noisy conditions it may fail to produce a clear output at all, and thus not make a decision.
This can be problematic for cognitive models that must form a clear decision (even when it may be incorrect).
The IA network might not be able to identify the correct winner as quickly or as reliably (depending on the choice of $\tau_1$), but given enough time it will eventually arrive at a decision and produce a clear output.
This is a direct consequence of the thresholding on the state feedback, which prevents competition from occurring until a sufficient amount of evidence has accumulated.
This also enables the IA network to react to small inputs.
In addition, the IA network is easily extendible to allow dynamic control of the decision speed, by supplying an external bias to layer 2 to adjust the $\vartheta$ threshold.

@@

\section{Notes}
Source code and supplementary analysis are available at \url{https://github.com/ctn-waterloo/cogsci17-decide}.
%These have not been peer reviewed.
